---
title: "InSituASProfile"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{InSituASProfile}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(InSituASProfile)
```

## Example

This is a basic example of how to use the InSituASProfile Package:

Import data (csv files) from folder and combine in single data frame for analysis. 

```{r import data}

InSituASProfile::import_data("C:/Users/lasse/OneDrive/skrivebord/gps_data", Velocity, Acceleration)

```

## Prepare data

This step cleans the data frame by 1) omitting all acceleration
values below 0, 2) identify the two highest acceleration values for every 
consecutive 0.2 m/s cut starting from 3 m/s, and 3) create an initial 
regression line and associated preliminary plot (if not FALSE) 

```{r prepare data}

InSituASProfile::prepare_data(data_import, print_plot = TRUE)

```

## Calculate the AS Profile

Calculate the A-S Profile. This step uses the data exported from prepare_data,
and to calculate the A-S Profile. It plots the A-S Profile as default (TRUE), 
while a plot showing the regression line is not printed by default (FALSE).

```{r calculate AS Profile}

InSituASProfile::get_AS_Profile(print_plot_regression_line = FALSE, print_AS_plot = TRUE)

```
